Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-06 analysis/paper/paper.qmd
add table 1; clean up word template

  echo: true

@@

We measured hydrology at each survey station. Conductivity and temperature in the water column were measured using a Sea-Bird Inc. SBE-9/11+ CTD profiler (Table 1). We used Niskin sampling bottles to collect water samples for measuring chlorophyll *a* (chl *a*) and phaeopigment concentrations (Table 1). For full details, see @dietrich2021winter.

@@

We used linear regression to quantify the relationship between the retained NMDS axes and the environmental, biological, and temporal variables. We performed this analysis with the `envfit()` function in the 'vegan' package, which treats environmental variables as the response variables and NMDS ordination scores as the predictors. The environmental variables included physical conditions (hydrology and ice conditions), biology (macrozooplankton community), and temporal variables (Table 1). Temporal variables included time of day of the net tow, to account for diel patterns in macrozooplankton distribution, as well as year, to account for interannual variability. The regression coefficients obtained from the analysis represent the direction and magnitude of the maximal change in community structure associated with each environmental variable. We tested for significant associations between predator and macrozooplankton communities using a chi-squared test and assessed the statistical significance of individual predator–prey community associations via post hoc analysis of the Pearson residuals.

@@

@@

<!-- The following line inserts a page break  -->

>>>>

  echo: false

@@

We measured hydrology at each survey station. Conductivity and temperature in the water column were measured using a Sea-Bird Inc. SBE-9/11+ CTD profiler [@tbl-envvar]. We used Niskin sampling bottles to collect water samples for measuring chlorophyll *a* (chl *a*) and phaeopigment concentrations [@tbl-envvar]. For full details, see @dietrich2021winter.

@@

We used linear regression to quantify the relationship between the retained NMDS axes and the environmental, biological, and temporal variables. We performed this analysis with the `envfit()` function in the 'vegan' package, which treats environmental variables as the response variables and NMDS ordination scores as the predictors. The environmental variables included physical conditions (hydrology and ice conditions), biology (macrozooplankton community), and temporal variables [@tbl-envvar]. Temporal variables included time of day of the net tow, to account for diel patterns in macrozooplankton distribution, as well as year, to account for interannual variability. The regression coefficients obtained from the analysis represent the direction and magnitude of the maximal change in community structure associated with each environmental variable. We tested for significant associations between predator and macrozooplankton communities using a chi-squared test and assessed the statistical significance of individual predator–prey community associations via post hoc analysis of the Pearson residuals.

@@

We are grateful for the diligent work by the field personnel who made these surveys possible, including the captains, crew, and support personnel of the RVIB ‘Nathaniel B. Palmer’. The surveys were conducted by a partnership of NOAA Fisheries Antarctic Ecosystem Research Division and the NSF US Antarctic Program (NSF Office of Polar Programs project 2011285). We thank Dr. Jack Conroy for his contributions and feedback on matters related to zooplankton communities. J.A.S. thanks M. P. Force and A. Borker for their dedicated support during the visual surveys

# Tables

<!-- Note: cross-referencing a table breaks column alignment. See https://github.com/quarto-dev/quarto-cli/issues/8970 -->

| Variable                   | Description and units                                                                                                                                                                                                                                                                                                 | Collection location |
|:-----------------|:------------------------------------|:-----------------|
| UML depth                  | Depth at which the density differed by 0.05 kg m^−3^ from the average density of the upper 10 m of the water column [@mitchell1991] \[meters\]                                                                                                                                                                        | Station             |
| Temperature                | Average UML temperature \[°C\]                                                                                                                                                                                                                                                                                        | Station             |
| Salinity                   | Average UML salinity \[PSU\]                                                                                                                                                                                                                                                                                          | Station             |
| Chl *a*                    | Average integrated chl *a* to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                         | Station             |
| Phaeopigment               | Average integrated phaeopigment to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                    | Station             |
| Ice type                   | Factor with 4 levels: open, thin, first-year, multi-year                                                                                                                                                                                                                                                              | Transect            |
| Ice coverage               | Percent cover                                                                                                                                                                                                                                                                                                         | Transect            |
| Macrozooplankton community | Factor with 5 levels corresponding to the clusters identified by @dietrich2021winter: 1 (*Salpa* and *Clione*), 2a (small *Euphausia*, myctophid larvae, and amphipods), 2b (*Thysanoessa*), 3a (extremely diverse, including siphonophores, chaetognaths, copepods), and 3b (*E. superba* and *E. crystallorophias*) | Station             |

: Environmental variables collected during survey. Hydrographic variables (upper mixed layer [UML] depth, temperature, salinity, chlorophyll a [chl a], and phaeopigment) were collected at sampling stations. Ice variables (type and coverage) were collected along transects and associated with the nearest station. Macrozooplankton communities were classified based on net tows collected at the sampling stations (see @dietrich2021winter). {#tbl-envvar} {tbl-colwidths="[20,60,20]"}

@@
